Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added biploar disorders positive diagnosis by sample chunk

>>>>

```{r Get Bipolar disorders positive by sample}

dat.retro_BD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)

dat.retro_BD_by_sample <- dat.retro_BD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Bipolar disorders" = n())
